Analysis

### 2023-04-24 analysis/analysis.Rmd

The data set for the 14C sum calibration is composed of the above-mentioned sources.

@@

Next, we calibrate the 14C data using rcarbon: <!--# uncal vs cal? -->

@@

```{r}
plot(1950-sumcal$grid$calBP, sumcal$grid$PrDens,type="l", main = paste0("n=", length(c14.calibrated)))

```

@@

```{r}
all_proxies[,2:5] <- all_proxies[,2:5] %>% scale() %>% diff() %>% rbind(0,.)
```

@@

```{r}
redux_factor <- 1
redux_nrow <- round(nrow(all_proxies) * redux_factor)
redux_seq <- round(seq(from=1,to=nrow(all_proxies), length.out = redux_nrow))

model_data <- all_proxies[redux_seq,]
```

>>>>

The data set for the 14C sum calibration is composed of the above-mentioned sources. This data consists of 1135 dates from 246 sites.

@@

Next, we calibrate the 14C data using rcarbon:

@@

```{r}
plot(1950-sumcal$grid$calBP, sumcal$grid$PrDens,type="l")
```

@@

```{r}
all_proxies_diff <- all_proxies
all_proxies_diff[,2:5] <- all_proxies_diff[,2:5] %>% scale() %>% diff() %>% rbind(0,.)
```

We can also visualise these deltas of the proxies:

```{r}
all_proxies_diff %>% pivot_longer(2:5) %>% ggplot(aes(x = age, y = value)) + geom_line() + facet_wrap(. ~ name)
```

@@

```{r}
redux_factor <- 1
redux_nrow <- round(nrow(all_proxies_diff) * redux_factor)
redux_seq <- round(seq(from=1,to=nrow(all_proxies_diff), length.out = redux_nrow))

model_data <- all_proxies_diff[redux_seq,]
```
